The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-15 paper.tex
update

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a radius of about 6.8 kpc along the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.

>>>>

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles.
